---
title: "Cabbages"
author: "sonya soto"
date: "summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$h_0$: there is no difference in the average of vitamin C content.   
$h_A$: there is a difference of vitamin c content of c52 and c39.   
# Methods    
We are explaining the vitamin c numerical variable by examining the categorical variable cultivation.  We are explaining the vitamin c numerical variable by examining the categorical variable cultivation 
<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```
The category c39 for cultivating had an overall lower mean for the numerical result of vitamin C. while the c52 category had a higher mean of the vitamin c using their cultivation method. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The cultivating method c39 had a mean of 51.5, C52 had a mean of 64.4   
## Inferential Results
  
```{r}
t.test(VitC~Cult,data=veggy)
```
based on our two sample T tests we can inter that the p-is 0.00000003405, from this we can reject the null hypothesis because of the sample result was very unlikely, meaning that the null hypothesis rejected.  

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->





The difference between the two categories we had, cultivative methods c39 and c52 were found to have a numerical difference of the vitamin c produced in the cabbages made. we rejected the null hypothesis after seeing the results of the t test. The c39 had a mean of 51.5 while the c52 group had a mean of 64.5. our p value from this was 0.00000003405.  